HPC--101\\Onboarding

### 2016-03-22 hpc_101/paper.tex
Introduction of a GPU submission script to the slide deck

>>>>

\subsection{MPI Batch Job Example Script}
\begin{frame}[fragile]
\frametitle{SLURM sbatch -- Submission Script File -- GPU}
\begin{semiverbatim}\tiny
[login lus]\$ cat gpu.slurm

\#!/bin/bash
\#SBATCH \ddash{}job-name=GPU\_example
\#SBATCH \ddash{}partition=gpu.q
\#SBATCH \ddash{}time=3-00:00:00 ## time format is DD-HH:MM:SS
\#\# task-per-node x cpus-per-task should not typically exceed core count on an individual node 
\#SBATCH \ddash{}nodes=1
\#SBATCH \ddash{}tasks-per-node=1
\#SBATCH \ddash{}cpus-per-task=10
\#SBATCH \ddash{}gres=gpu:NV-K40:2  \#\# request both GPUs in the GPU node.
\#\#\# To request only 1 of the two GPUs in the node, you would do: gpu:NV-K40:1
\#SBATCH \ddash{}error=hello-\%A.err \#\# \%A - filled with jobid
\#SBATCH \ddash{}output=hello-\%A.out \#\# \%A - filled with jobid
\#\# Useful for remote notification
\#SBATCH \ddash{}mail-type=BEGIN,END,FAIL,REQUEUE,TIME\_LIMIT\_80
\#SBATCH \ddash{}mail-user=user@test.org

source \ctilde/.bash_profile \#if you want to use modules or need environment variables, source your bash profile
module load GPGPU/cuda/samples/7.5

bandwidthTest; cudaOpenMP; deviceQuery; simpleMultiGPU
\end{semiverbatim}
\end{frame}
